---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo=FALSE}
library(tldr)
```

This package gives a number of functions to aid common data analysis processes and reporting statistical results in an RMarkdown file. Data analysis functions combine multiple base R functions used to describe simple bivariate relationships into a single, easy to use function. Reporting functions will return character strings to report p-values, confidence intervals, and hypothesis test and regression results. Strings will be LaTeX-formatted as necessary and will knit pretty in an RMarkdown document. The package also provides a wrapper for the CreateTableOne function in the tableone package to make the results knitable.

## Data analysis functions

- `cat_compare()`

Suppose we have the following data:

```{r, warning=FALSE}
x = rnorm(50)
y = rnorm(50)
a = sample(letters[1:3], size=50, replace=TRUE)
b = sample(letters[4:6], size=50, replace=TRUE)
```

We can investigate the relationship betweewn `a` and `b` using `cat_compare()`:

```{r}
cat_compare(y=b, x=a, title='Relationship between a and b')
```


## `inline` and `write` functions

- `inline_test()`
- `inline_reg()`
- `inline_coef()`
- `inline_anova()`
- `write_int()`
- `write_p()`

Using the data above, we can obtain some inferential results:

```{r, warning=FALSE}
x = rnorm(50)
y = rnorm(50)
a = sample(letters[1:3], size=50, replace=TRUE)
b = sample(letters[1:3], size=50, replace=TRUE)

test1 = t.test(x)
test2 = chisq.test(table(a,b))
model1 = lm(y ~ x)
model2 = lm(y ~ a)
```

We can then report the results of the hypothesis test inline using `inline_test(test1)` and get the following: `r inline_test(test1)`.  Simiarly, `inline_test(test2)` will report the results of the chi-squared test: `r inline_test(test2)`. So far `inline_test` only works for $t$ and chi-squared tests, but the goal is to add more functionality - requests gladly accepted.

The regression results can be reported with `inline_reg(model1)` and `inline_coef(model1, 'x')` to get `r inline_reg(model1)` and `r inline_coef(model1, 'x')`, respectively. In addition, `inline_anova(model2)` will report the ANOVA F statistic and relevant results: `r inline_anova(model2)`. So far `inline_reg` and `inline_coef` currently work for `lm` and `glm` objects; `inline_anova` only works for `lm` objects.

We can also report the confidence intervals using `write_int()` with a length-2 vector of interval endpoints. For example, `write_int(c(3.04, 4.7))` and `write_int(text1$conf.int)` yield `r write_int(c(3.04, 4.7))` and `r write_int(test1$conf.int)`, respecively.

P-values can be reported using `write_p()`. This function will take either a numeric value or a list-like object with an element named `p.value`. For example, `write_p(0.00002)` gives `r write_p(0.00002)` and `write_p(test1)` gives `r write_p(test1)`.

See the help files of all functions described above for more details and options. For example, all test and regression reporting functions have wrappers ending in `_p` which report only the p-value of the input.


## `KreateTableOne`

The package also provides the function `KreateTableOne`, a wrapper for `CreateTableOne` from the `tableone` package which makes the results knitable. First use `KreateTableOne` in an R chunk with `results='hide'` (or ouside the RMarkdown document), then recall the saved data frame in a new chunk.  For example:

```{r, results='hide'}
table1 = KreateTableOne(x=mtcars, strata='am', 
                        factorVars='vs')
colnames(table1)[1:2] = c('am = 0', 'am = 1')
```

Then

```{r}
knitr::kable(table1[, 1:3], align='r')
```